animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2024-01-12 animbook-journal.Rmd
more examples

```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
p <- wallaby_plot(data = animbook,
             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
             shade_palette = c("#737373", "#969696", "#BDBDBD",
                               "#D9D9D9","#D9D9D9","#D9D9D9"),
             rendering = "gganimate",
             subset = "top",
             relation = "one_many",
             total_point = NULL)

@@

>>>>

```{r, echo=TRUE, fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
p <- wallaby_plot(data = animbook,
             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
             rendering = "gganimate",
             subset = "top",
             relation = "one_many",
             total_point = NULL)

@@

  Additionally, users have the flexibility to explore various options, such as subset or relation, allowing them to customize how the plot will appear.

```{r}
p_2 <- wallaby_plot(data = animbook,
                   rendering = "gganimate",
                   subset = "top",
                   relation = "many_one",
                   total_point = NULL)

p_2

p_3 <- wallaby_plot(data = animbook,
                    rendering = "gganimate",
                    subset = "B",
                    relation = "many_one",
                    total_point = NULL)

p_3
```

### 2024-01-12 animbook-journal.tex
more examples

\begin{verbatim}
p <- wallaby_plot(data = animbook,
             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
             shade_palette = c("#737373", "#969696", "#BDBDBD",
                               "#D9D9D9","#D9D9D9","#D9D9D9"),
             rendering = "gganimate",
             subset = "top",
             relation = "one_many",
             total_point = NULL)

@@

>>>>

\begin{verbatim}
p <- wallaby_plot(data = animbook,
             group_palette = RColorBrewer::brewer.pal(9, "Set1"),
             rendering = "gganimate",
             subset = "top",
             relation = "one_many",
             total_point = NULL)

@@

Additionally, users have the flexibility to explore various options, such as subset or relation, allowing them to customize how the plot will appear.

\includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-11-1.pdf} \includegraphics{animbook-journal_files/figure-latex/unnamed-chunk-11-2.pdf}
